\documentclass[a4paper,11pt]{article}
\usepackage[affil-it]{authblk}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[footnotesize]{caption2}
\usepackage{threeparttable}
\usepackage{booktabs,tabularx}
\usepackage{multirow}
\usepackage{indentfirst}
\usepackage{cite}
\usepackage{enumerate}
\usepackage[bookmarksnumbered=true,
            bookmarksopen=true,
            colorlinks=true,
            citecolor=blue,
            linkcolor=red,
            anchorcolor=green,
            urlcolor=blue
           ]{hyperref}
\setlength{\hoffset}{-0.54cm}
\setlength{\voffset}{-0.54cm}
\setlength{\oddsidemargin}{0.5cm}
\setlength{\evensidemargin}{0.5cm}
\setlength{\textwidth}{16cm}
\setlength{\topmargin}{0cm}
\setlength{\headheight}{0.55cm}
\setlength{\headsep}{0.45cm}
\setlength{\footskip}{0.90cm}
\setlength{\textheight}{23.8cm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{remark}{Remark}
\newenvironment{proof}{\begin{trivlist} \item[]{\em Proof.}}{\end{trivlist}}
\renewcommand\tablename{\bf{Table}}
\renewcommand\figurename{\bf{Figure}}
\title{\bf{Title}}
\author[1]{Author1\thanks{\url{MailTo:yqlian.rol@gmail.com}}}
\author[1]{Author2}
\affil[1]{Institution}
\date{}
\begin{document}
\maketitle
\pagestyle{plain}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Abstract
\vskip .2in \noindent {\bf Key Words:} Model, Analysis, Sampling.
\end{abstract}

\section{Introduction}
Introduction

\section{Preliminaries}
Preliminaries

\section{Analysis}
Analysis

\subsection{Analysis A}
Analysis A

\subsection{Analysis B}
Analysis B

\begin{proof}
The same as Theorem 1.
\end{proof}

\section{Numerical Studies}
Samples

\section{Conclusion}
Conclusion

\begin{thebibliography}{99}
\bibitem{Berger1} Berger, J.O. and Bernardo, J.M. (1992). ~Ordered group reference priors with applications to a multinomial problem. ~{\it Biometrika}, 79, 25-37.
\bibitem{Berger2} Berger, J.O. and Bernardo, J.M. (1992). ~On the development of reference priors. ~{\it Bayesian Statistics}, 4, 35-60.
\end{thebibliography}

\end{document}
